---
output:
  html_document: default
  pdf_document: null
  word_document: null
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<center>
<h2> <b> STRUDEL FIDELITY RESEARCH ANALYSIS</b> </h2>
<h3> Dr. Ritter, Fredrick Ryans, Martin Yeh </h3>
<h3> 08/14/2020 </h3>
</center>

#### **PROJECT DESCRIPTION**
  <h4>What is the effect of level of simulation fidelity on learning
  and then on performance in the target task? We consider an
  example of an electronic maintenance training system with
  two levels of fidelity: a high fidelity (HiFi) simulation that
  basically takes as much time as the real-world task and a low
  fidelity (LoFi) simulation with minimal delays and many
  actions removed or reduced in fidelity and time. The LoFi
  simulation initially takes about one quarter of the time, and
  thus starts out providing about four times as many practice
  trials in a given time period. The time to perform the task
  modifies the learning curves for each system. The LoFi curve
  has a lower intercept and a steeper slope. For a small number
  of practice trials, this makes a significant difference. For
  longer time periods, the differences between low and high
  fidelity get smaller. Learners that move from low to high
  appear to not be adversely affected. We note factors that
  could influence this transfer (i.e., subtasks included in each
  simulation), and how this approach could be extended
  
  <br><br>
  This document is a visual analysis of the Strudel data models provided
  in the Ritter paper: fidelity on learning.
  </h4>


##### **Link To Paper:** [Click Here](http://acs.ist.psu.edu/papers/ritterM20.pdf)

<br>

### Libraries
```{r message=FALSE}
library(dplyr)
library(ggplot2)
library(tidyr)

options(digits =2, max.print=1000000)
```

## Results {.tabset}

### FIG 1
<center>
```{r echo=FALSE}
# This plot displays a simple learning curve plot of 1-10 trials using the response function from strudel analysis.

# Variables for response function
alpha = 0.02
fixedTasks = 26
learnedTasks = 32.75

# Data frame is the data structure used to store data for visualize plots 
learning_curve = data.frame(
  labels = c(1:10),
  respFunc = fixedTasks + (learnedTasks*((c(1:10))^-alpha))
)

ggplot(learning_curve, aes(x = labels, y = respFunc)) +
  labs(
    x = "Trials", y = "Response Time(s)",
    title = "Learning Curve Plot", 
    subtitle = "Figure 1",
    caption = "Figure 1: This plot displays a simple learning curve plot of 1-10\n trials using the response function from strudel analysis.") +
  geom_line(color="green", size=1) + 
  geom_point(size = 2) +
  ylim(57, 60) +
  scale_x_continuous(breaks=c(1:10)) + 
  theme(
    axis.text=element_text(size=14,face="bold"),
    axis.title=element_text(size=14,face="bold"),
    legend.title=element_blank(), 
    plot.title = element_text(color = "red", size = 16, face = "bold", hjust = 0.5),
    plot.subtitle = element_text(color = "blue", hjust = 0.5),
    plot.caption = element_text(color = "black", size = 14, hjust = 0.5))

```
</center>

### FIG 2
<center>
``` {r echo=FALSE}
# This plot displays a learning curve plot of 1-2000 trials using the response function   from strudel analysis.

# Data frame is the data structure used to store data for visualize plots 
larger_learning_curve = data.frame(
  labels = c(1:2000),
  respFunc = fixedTasks + (learnedTasks*((c(1:2000))^-alpha))
)

# Visualization and construction of plot
ggplot(larger_learning_curve, aes(x = labels, y = respFunc)) + 
  labs(
    x = "Trials", y = "Response Time(s)",
    title = "Larger Learning Curve Plot (1-2000 Datapoints)", 
    subtitle = "Figure 2",
    caption = "Figure 2: This plot displays a learning curve plot of 1-2000\n trials using the response function from strudel analysis.") +
  geom_line() +
  geom_point(size=1) +
  theme(axis.text=element_text(size=14,face="bold"),axis.title=element_text(size=14,face="bold")) +
  theme(
    legend.title=element_blank(), 
    plot.title = element_text(color = "red", size = 16, face = "bold", hjust = 0.5),
    plot.subtitle = element_text(color = "blue", hjust = 0.5),
    plot.caption = element_text(color = "black", size = 14, hjust = 0.5))

```
</center>

### FIG 3
<center>
``` {r echo=FALSE}
# This plot displays a Hifi and Lofi plot from strudel analysis.

# Data frame is the data structure used to store data for visualize plots 
two_line_plot = data.frame( #Use function to generate plots
  time_blocks = c(1:10),
  lofi_resp_time = c(11.8,5.5,4.3,3.8,3.5,3.2,3.1,2.9,2.8,2.7),
  hifi_resp_time = c(13.75,7.807,5.544,4.756,4.316,4.022,3.805,3.635,3.497,3.382)
)

# Visualization and construction of plot
ggplot(two_line_plot, aes(x=time_blocks)) +
  geom_line(aes(y=lofi_resp_time, color="Lofi"), size = 1)+ 
  geom_line(aes(y=hifi_resp_time,color="Hifi"),size=1) + 
  labs(
    x = "Trials", y = "Response Time(s)",
    title = "HiFi and LoFi Curves", 
    subtitle = "Figure 3",
    caption = "Figure 3: This plot displays a Hifi and Lofi plots.") + 
  scale_x_continuous(breaks=c(1:10)) +
  theme(
    axis.text=element_text(size=14,face="bold"),
    axis.title=element_text(size=14,face="bold"),
    legend.title=element_blank(), 
    legend.text=element_text(size=14),
    plot.title = element_text(color = "red", size = 16, face = "bold", hjust = 0.5),
    plot.subtitle = element_text(color = "blue", hjust = 0.5),
    plot.caption = element_text(color = "black", size = 14, hjust = 0.5))
```
</center>

### FIG 4
<center>
``` {r echo=FALSE}
# This plot displays a 3 learning curve plots of 1-10 trials using the response function and data from strudel analysis.

# Variables for response function
alpha = .20
fixedTasks = 26
learnedTasks = 32.75

# Data frame is the data structure used to store data for visualize plots 
multi_learning_curve = data.frame(
  labels = c(1:10),
  respFunc = fixedTasks + (learnedTasks*((c(1:10))^-alpha)),#Function working for this
  respFunc2 = c(40.5,37.4,36,35.2,34.6,34.1,33.8,33.5,33.2,33),#Change to working function
  respFunc3 = c(23.3,14.5,13.1,12.4,12,11.7,11.5,11.3,11.1,11)#Change to working function
)

# Visualization and construction of plot
ggplot(multi_learning_curve, aes(x = labels)) + 
  geom_line(aes(y = respFunc, color="High", group= 1), size = 2) +
  geom_line(aes(y = respFunc2, color="Low", group= 2), size = 2) +
  geom_line(aes(y = respFunc3, color="Low-to-High", group= 3), size = 2) +
  labs(
    x = "Trials", y = "Response Time (s)",
    title = "Multi-Complex Learning Curve Plot", 
    subtitle = "Figure 4",
    caption = "Figure 4: This plot displays a 3 learning curve plots of 1-10 trials.") + 
  scale_x_continuous(breaks=c(1:10)) +
  theme(axis.text=element_text(size=14,face="bold"),axis.title=element_text(size=14,face="bold")) +
  theme(
    legend.title=element_blank(), 
    legend.text=element_text(size=14),
    plot.title = element_text(color = "red", size = 16, face = "bold", hjust = 0.5),
    plot.subtitle = element_text(color = "blue", hjust = 0.5),
    plot.caption = element_text(color = "black", size = 14, hjust = 0.5))

```
</center>

### FIG 5
<center>
``` {r echo=FALSE}
# This plot displays fault mixed learning plot using the data from strudel analysis.

# Data frame is the data structure used to store data for visualize plots 
fault_mixed_learning_plot = data.frame(
  labels = c("Low", "High", "HHap", "RWhu", "RWHap"),
  data = c(23.3,58.75,0,0,0)
)

sorted_labels = factor(fault_mixed_learning_plot$labels,levels = c("Low", "High", "HHap", "RWhu", "RWHap"))# Sorts labels using factor function 

# Visualization and construction of plot
ggplot(fault_mixed_learning_plot, aes(x = sorted_labels, y = data, color=sorted_labels, group= 1)) + 
  geom_line() +
  geom_point(size = 4) +
  labs(
    x = "Interface Type",y = "Time Per Trial",
    title = "Simple Fault Mixed Learning Plot", 
    subtitle = "Figure 5",
    caption = "Figure 5: This plot displays fault mixed learning plot.") + 
  theme(axis.text=element_text(size=14,face="bold"),axis.title=element_text(size=14,face="bold")) +
  theme(
    legend.title=element_blank(),
    legend.text=element_text(size=14),
    plot.title = element_text(color = "red", size = 16, face = "bold", hjust = 0.5),
    plot.subtitle = element_text(color = "blue", hjust = 0.5),
    plot.caption = element_text(color = "black", size = 14, hjust = 0.5))
```
</center>

### FIG 6
<center>
``` {r echo=FALSE}
# This plot displays a second fault mixed learning plot using the data from strudel analysis.

# Data frame is the data structure used to store data for visualize plots 
fault_mixed_learning_plot_v2 = data.frame(
  labels = c("Low", "High", "HHap", "RWhu", "RWHap"),
  data = c(2.6,1,0,0,0)
)

sorted_labels = factor(fault_mixed_learning_plot_v2$labels,levels = c("Low", "High", "HHap", "RWhu", "RWHap"))# Sorts labels using factor function 

# Visualization and construction of plot
ggplot(fault_mixed_learning_plot_v2, aes(x = sorted_labels, y = data, color=sorted_labels, group= 1)) + 
  geom_line() +
  labs(
    x = "Interface Type", y = "Time Per Trial",
    title = "Simple Fault Mixed Learning Plot v2", 
    subtitle = "Figure 6",
    caption = "Figure 6: This plot displays a second fault mixed learning plot.") + 
  geom_point(size = 4) +
  theme(axis.text=element_text(size=14,face="bold"),axis.title=element_text(size=14,face="bold")) +
  theme(
    legend.title=element_blank(), 
    legend.text=element_text(size=14),
    plot.title = element_text(color = "red", size = 16, face = "bold", hjust = 0.5),
    plot.subtitle = element_text(color = "blue", hjust = 0.5),
    plot.caption = element_text(color = "black", size = 14, hjust = 0.5))

```
</center>

### FIG 7
<center>
``` {r echo=FALSE}
# This plot displays an interface combination plot using the data from strudel analysis.

rand_values = runif(2000, min=0, max=61)#Generates Random Values N=2000, i = 0-61

# Data frame is the data structure used to store data for visualize plots 
ui_combo_plot = data.frame(
  id = c(1:8),
  ui_combo = 	c("Lhu","LHap","Mhu","Mhap","Hhu","HHap","RWhu","RWHap"),		
  time_per_trial = c(11.75,12.95,15.95,15.95,13.75,35.4,60.25,60.25), 
  stringsAsFactors = FALSE
)
sorted_labels = factor(ui_combo_plot$ui_combo,levels = c("Lhu","LHap","Mhu","Mhap","Hhu","HHap","RWhu","RWHap"))

# Visualization and construction of plot
ggplot(ui_combo_plot, aes(sorted_labels,time_per_trial, group = 1, color=sorted_labels))+
  geom_line(color='black',size=1) +
  geom_point(size = 4) +
  labs(
    x = "User Interface Combination", y = "Times Per Trial (s)",
    title = "User Interface Combination Plot", 
    subtitle = "Figure 7",
    caption = "Figure 7: This plot displays an interface combination plot.") + 
  theme(axis.text=element_text(size=14,face="bold"),axis.title=element_text(size=14,face="bold")) +
  theme(
    legend.title=element_blank(), 
    legend.text=element_text(size=14),
    plot.title = element_text(color = "red", size = 16, face = "bold", hjust = 0.5),
    plot.subtitle = element_text(color = "blue", hjust = 0.5),
    plot.caption = element_text(color = "black", size = 14, hjust = 0.5))
```
</center>

### FIG 8
<center>
``` {r echo=FALSE}
# This plot displays an second interface combination plot using the data from strudel analysis.

# Data frame is the data structure used to store data for visualize plots 
ui_combo_plot_v2 = data.frame(
  id = c(1:8),
  ui_combo = 	c("Lhu","LHap","Mhu","Mhap","Hhu","HHap","RWhu","RWHap"),		
  time_per_trial = c(4.6,4.6,3.8,3.8,1.7,1.7,1,1)
)
sorted_labels = factor(ui_combo_plot_v2$ui_combo,levels = c("Lhu","LHap","Mhu","Mhap","Hhu","HHap","RWhu","RWHap"))

# Visualization and construction of plot
ggplot(ui_combo_plot_v2, aes(sorted_labels,time_per_trial, group = 1, color=sorted_labels))+
  geom_line(color='black',size=1) +
  geom_point(size = 4) +
  labs(
    x = "User Interface Combination", y = "Times Per Trial (s)",
    title = "User Interface Combination Plot v2", 
    subtitle = "Figure 8",
    caption = "Figure 8: This plot displays an second interface combination plot.") + 
  theme(axis.text=element_text(size=14,face="bold"),axis.title=element_text(size=14,face="bold")) +
  theme(
    legend.title=element_blank(), 
    legend.text=element_text(size=14),
    plot.title = element_text(color = "red", size = 16, face = "bold", hjust = 0.5),
    plot.subtitle = element_text(color = "blue", hjust = 0.5),
    plot.caption = element_text(color = "black", size = 14, hjust = 0.5))
```
</center>

### FIG 9
<center>
``` {r echo=FALSE, message=FALSE}
# specify log plot using ggplot
# Variables for response function
# plot(p,trans, ylim = c(0,1), ylab='coeff', log='x')

alpha = .20
fixedTasks = 26
learnedTasks = 32.75

# Data for putting inside dataframe 
trials = c(1:10)
RT = c(58.8,46.6,43.5,41.9,40.9,40.2,39.6,39.1,38.8,38.4)
trials_per_min = 60/RT
total_reps = c(10,13,26,40,54,69,84,99,115,130)#Generate data using formula in CSV file ( const + 10 * totals_reps)
log_base10 = log(total_reps, base=10)
low_values = c(43.1,40.3,38.9,38,37.4,36.9,36.6,36.2,36,35.7)#Generate data using formula in CSV file ( fixed + learned * (trials)^-alpha)
delta_Ln =c(1.411,0.441,0.456,0.464,0.469,0.473,0.476,0.478,0.480,0.481)

# Data frame is the data structure used to store data for visualize plots 
loglogPlot = data.frame(
trials,
trials_per_min,
RT, #rounded up because option rule at the top of R code
total_reps,
log_base10,
low_values,
delta_Ln
)

# Version 1: Visualization and construction of plot (Must transform plot to a log plot to measure distance between one point to another)
ggplot(loglogPlot, aes(x = trials)) + 
  geom_line(aes(y = RT, color="High", group= 1), size = 1) +
  geom_line(aes(y = low_values, color="Low to High", group= 1), size = 1) +
  geom_line(aes(y = delta_Ln, color="Low", group= 1), size = 1) +
  labs(
    x = "Blocks of 10 min.",
    y = "Response Time (s)",
    title = "Log Log Plot", 
    subtitle = "Figure 9",
    caption = "Figure 9: This plot displays a loglog plot.") + 
  scale_x_continuous(trans = 'log10') +
  scale_y_continuous(trans = 'log10') +
  annotation_logticks() +
  theme(axis.text=element_text(size=14,face="bold"),axis.title=element_text(size=14,face="bold")) +
  theme(
    legend.title=element_blank(), 
    legend.text=element_text(size=14),
    plot.title = element_text(color = "red", size = 16, face = "bold", hjust = 0.5),
    plot.subtitle = element_text(color = "blue", hjust = 0.5),
    plot.caption = element_text(color = "black", size = 14, hjust = 0.5))

print (loglogPlot)# Print data from log log dataframe

```
</center>

<!-- 
fixedTasks <- 10
learnedTasks <- 20
Learnable <- 10
learnedTasks <- 20
For totalreps = 1 to 1000
alpha <- .2

For totalreps = 1 to 1000
Points <- use formula
pointsA[totalresps] <- formula(….., totalReps)

parameters
Power law as a formula
generate the points
Plot the points

Result: 
Plot trials,pointsA
-->

### FIG 10
<center>
``` {r echo=FALSE, message=FALSE}
#THIS FIGURE APPLIES RESP FUNCTION OF 1-1000 POINTS

# Variables for response function
alpha = .20
fixedTasks = 26
learnedTasks = 32.75

datapoints = c(1:10) #generates a flattened list of 1-10 points (change to 1000 points)
Respfn = fixedTasks + (learnedTasks*((datapoints)^-alpha))#apply function to 10 datapoints (i.e., flattened list)

# Data frame is the data structure used to store data for visualize plots 
loglogPlot_v2 = data.frame(
 id = c(1:10),
 trials_per_min = c(1.0,1.3,1.4,1.4,1.5,1.5,1.5,1.5,1.5,1.6),
 data = Respfn
)

plot(x = loglogPlot_v2$id, y=loglogPlot_v2$data)

print (loglogPlot_v2)#  Basic plot of respFunc

#https://holtzy.github.io/Pimp-my-rmd/#tabs_for_sub-chapters
```
</center>

<!-- ### FIG 11
<center>
``` {r echo=FALSE, message=FALSE}

# Variables for response function
alpha = .20
fixedTasks = 26
learnedTasks = 4
learnable = 32.75

# Data for putting inside dataframe 
trials = c(1:10)
RT = c(58.8,46.6,43.5,41.9,40.9,40.2,39.6,39.1,38.8,38.4)
trials_per_min = 60/RT
total_reps = c(10,13,26,40,54,69,84,99,115,130)#Generate data using formula in CSV file ( const + 10 * totals_reps)
totalReps = c(26,64,105,149,194,240,287,334,382,431) # Generate data using strudel formula in CSV
RT_sec = c(23.3,15.8,14.4,13.8,13.3,13.0,12.8,12.6,12.5,12.3) # Generate data using strudel formula in CSV
formula = fixedTasks + learnedTasks + (learnable - learnedTasks)*(totalReps^-alpha)

# Data frame is the data structure used to store data for visualize plots 
loglogPlot_v3 = data.frame(
trials,
RT,
formula,
RT_sec
)

# Version 2: Visualization and construction of plot
ggplot(loglogPlot_v3, aes(x = trials)) + 
  geom_line(aes(y = RT, color="High", group= 1), size = 1) +
  geom_line(aes(y = formula, color="Low to High", group= 1), size = 1) +
  geom_line(aes(y = RT_sec, color="Low", group= 1), size = 1) +
  labs(
    x = "Blocks of 10 min.", y = "Response Time (s)",
    title = "Log Log Plot v3", 
    subtitle = "Figure 11",
    caption = "Figure 11: This plot displays a loglog plot v3.") + 
  scale_x_continuous(breaks=c(1:10)) +
  ylim(0, 70) +
  theme(axis.text=element_text(size=14,face="bold"),axis.title=element_text(size=14,face="bold")) +
  theme(
    legend.title=element_blank(), 
    legend.text=element_text(size=14),
    plot.title = element_text(color = "red", size = 16, face = "bold", hjust = 0.5),
    plot.subtitle = element_text(color = "blue", hjust = 0.5),
    plot.caption = element_text(color = "black", size = 14, hjust = 0.5))

print (loglogPlot_v3)# Print data from log log dataframe

#summary(loglogPlot)
#https://holtzy.github.io/Pimp-my-rmd/#tabs_for_sub-chapters
```

``` {r echo=FALSE, message=FALSE}
fidelity_df = data.frame(
  step0= c("Insert Fault"), 
  step1= c("Approach System"),
  step2= c("Open Cabinet"),
  step3= c("Ground Yourself"),
  step4= c("Check Front Panel"),
  step5= c("Choose Tray"),
  step6= c("Open Tray"),
  step7= c("Check Light"),
  step8= c("If off, have answer;If no, go to next light"),
  step9= c("Check Light;Overdriven Amp Fault"),
  step10= c("Recognize Fault"),
  step11= c("Indicate Fault")
)

#print (fidelity_df)

```


``` {r echo=FALSE, message=FALSE}
# SOURCES
# [1] https://holtzy.github.io/Pimp-my-rmd/#tabs_for_sub-chapters
# [2] https://en.wikipedia.org/wiki/Power_law_of_practice
# [3] https://www.statisticshowto.com/power-law/#:~:text=The%20power%20law%20(also%20called,4%20to%2016%20inches%20squared).

```
</center> -->

### UPDATES
* **Update 07/28/20**
  + Successfully sorted categorical data with factor function
  + Added more plots & better visualization aspects

* **Update 08/05/20** 
  + Added comments
  + Updated variables to be more description
  + Added more plots & better visualization aspects
  + Add default legend name, and key (no documentation found on this that works)
  + Learn to plot
 Read log/log plot and create complex graph
 Help function: help("ggplot")
 Change code to reflect 

* **Update 08/11/20**
  + ! Need to change plot number system from double to int on x/y axis. 
  + ! Unsuccessful with reading alpha input for various value calculations
  + Save plots via code ggplot(), next phase to generate automated reports 
  + Corrected x,y axis labels to
  + ! Reading on log log plots, and trying to compute 
 Change legend title to blank

* **Update 08/14/20**
  + Create reports using R markdown
  + Updated errors, bugs, aesthetics

* **Update 08/17/20**
  + Updated x,y axis to be int not float
  + Updated errors, bugs, aesthetics
  
* **Update 08/25/20**
  + Updated version control
  + Constructed log graph using power law formula
  + Commented plots in code
  + ! Add descriptions to plots, rename plots
  + ! Generate complex plots from strudel analysis
  + ! Add task analysis from strudel into a matrix in R
  
* **Update 08/27/20**
  + Added labels description to Strudel plots
  + Renamed Strudel plots
  + Changed label visualization
  
* **Update 09/02/20**
  + Constructed log log plot from strudel analysis
  + Updated plots visualizations
  
* **Update 09/09/20**
  + ! Make x.y labels bigger
  + ! Use function to generate 1000 trials
  + ! Change high to lo labels and low labels fig 9-11

## {-}

&nbsp;
<hr />
<h4 style="text-align: center;">Programming done by <a href="https://github.com/gremlokk/">Fredrick Ryans</a></h4>
<h4 style="text-align: center;"><span style="color: #808080;">Email: <em>fxr5077@psu.edu</em></span></h4>
<h4 style="text-align: center;"><a href="http://acs.ist.psu.edu/wp/"> >> Applied Cognitive Science Lab << </a></h4>

<!-- Add icon library -->
<link rel="stylesheet" href="https://cdnjs.cloudflare.com/ajax/libs/font-awesome/4.7.0/css/font-awesome.min.css">

<!-- Add font awesome icons -->
<h2 style="text-align: center;">
    <a href="https://www.linkedin.com/in/fryans" target = "_blank" class="fa fa-linkedin"></a>
    <a href="https://github.com/gremlokk/" target = "_blank" class="fa fa-github"></a>
</h2>

&nbsp;
