---
output:
  html_document: default
  pdf_document: null
  word_document: null
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<center>
<h2> <b> STRUDEL FIDELITY RESEARCH ANALYSIS</b> </h2>
<h3> Dr. Ritter, Fredrick Ryans, Martin Yeh </h3>
<h3> 08/14/2020 </h3>
</center>

#### **NOTES**
 This document is a visual analysis of the Strudel data models provided
 in the Ritter paper: fidelity on learning.

##### **Link To Paper:** [Click Here](http://acs.ist.psu.edu/papers/ritterM20.pdf)

<br>

##### **MAJOR UPDATES**

* **Update 07/28/20**
  + Successfully sorted categorical data with factor function
  + Added more plots & better visualization aspects

* **Update 08/05/20** 
  + Added comments
  + Updated variables to be more description
  + Added more plots & better visualization aspects
  + Add default legend name, and key (no documentation found on this that works)
  + Learn to plot
 Read log/log plot and create complex graph
 Help function: help("ggplot")
 Change code to reflect 

* **Update 08/11/20**
  + ! Need to change plot number system from double to int on x/y axis. 
  + ! Unsuccessful with reading alpha input for various value calculations
  + Save plots via code ggplot(), next phase to generate automated reports 
  + Corrected x,y axis labels to
  + ! Reading on log log plots, and trying to compute 
 Change legend title to blank

* **Update 08/14/20**
  + Create reports using R markdown
  + Updated errors, bugs, aesthetics

* **Update 08/17/20**
  + Updated x,y axis to be int not float
  + Updated errors, bugs, aesthetics
  
* **Update 08/25/20**
  + Updated version control
  + Constructed log graph using power law formula
  + Commented plots in code
  + ! Add descriptions to plots, rename plots
  + ! Generate complex plots from strudel analysis
  + ! Add task analysis from strudel into a matrix in R
  
* **Update 08/27/20**
  + Added labels description to Strudel plots
  + Renamed Strudel plots
  + Changed label visualization
  
<br>

### Libraries
```{r message=FALSE}
library(dplyr)
library(ggplot2)
library(tidyr)

# options(max.print=1000000)
```

## Results {.tabset}

### FIG 1
<center>
```{r echo=FALSE}
# This plot displays a simple learning curve plot of 1-10 trials using the response function from strudel analysis.

# Variables for response function
alpha = 0.02
fixedTasks = 26
learnedTasks = 32.75

# Data frame is the data structure used to store data for visualize plots 
learning_curve = data.frame(
  labels = c(1:10),
  respFunc = fixedTasks + (learnedTasks*((c(1:10))^-alpha))
)

ggplot(learning_curve, aes(x = labels, y = respFunc)) +
  #labs(x = "Trials", y = "Response Time") + #response time, task time
  labs(x = "Trials", y = "Response Time",
       title = "Learning Curve Plot", 
       subtitle = "Figure 1",
       caption = "Figure 1: This plot displays a simple learning curve plot of 1-10\n trials using the response function from strudel analysis.") +
  geom_line(color="green", size=1) + 
  geom_point(size = 2) +
  ylim(57, 60) +
  scale_x_continuous(breaks=c(1:10)) + 
  theme(legend.title=element_blank(), 
  plot.title = element_text(color = "red", size = 16, face = "bold", hjust = 0.5),
  plot.subtitle = element_text(color = "blue", hjust = 0.5),
  plot.caption = element_text(color = "black", size = 12, hjust = 0.5))

```
</center>

### FIG 2
<center>
``` {r echo=FALSE}
# This plot displays a learning curve plot of 1-2000 trials using the response function   from strudel analysis.

# Data frame is the data structure used to store data for visualize plots 
larger_learning_curve = data.frame(
  labels = c(1:2000),
  respFunc = fixedTasks + (learnedTasks*((c(1:2000))^-alpha))
)

# Visualization and construction of plot
ggplot(larger_learning_curve, aes(x = labels, y = respFunc)) + 
  labs(x = "Trials", y = "Response Time(s)",
       title = "Larger Learning Curve Plot (1-2000 Datapoints)", 
       subtitle = "Figure 2",
       caption = "Figure 2: This plot displays a learning curve plot of 1-2000\n trials using the response function from strudel analysis.") +
  geom_line() +
  geom_point(size=1) +
  theme_bw() + 
  theme(legend.title=element_blank(), 
  plot.title = element_text(color = "red", size = 16, face = "bold", hjust = 0.5),
  plot.subtitle = element_text(color = "blue", hjust = 0.5),
  plot.caption = element_text(color = "black", size = 12, hjust = 0.5))

```
</center>

### FIG 3
<center>
``` {r echo=FALSE}
# This plot displays a Hifi and Lofi plot from strudel analysis.

# Data frame is the data structure used to store data for visualize plots 
two_line_plot = data.frame( #Use function to generate plots
  time_blocks = c(1:10),
  lofi_resp_time = c(11.8,5.5,4.3,3.8,3.5,3.2,3.1,2.9,2.8,2.7),
  hifi_resp_time = c(13.75,7.807,5.544,4.756,4.316,4.022,3.805,3.635,3.497,3.382)
)

# Visualization and construction of plot
ggplot(two_line_plot, aes(x=time_blocks)) +
  geom_line(aes(y=lofi_resp_time, color="Lofi"), size = 1)+ 
  geom_line(aes(y=hifi_resp_time,color="Hifi"),size=1) + 
  labs(x = "Trials", y = "Response Time(s)",
       title = "HiFi and LoFi Curves", 
       subtitle = "Figure 3",
       caption = "Figure 3: This plot displays a Hifi and Lofi plots.") + 
  scale_x_continuous(breaks=c(1:10)) +
  theme_bw() + 
  theme(legend.title=element_blank(), 
  plot.title = element_text(color = "red", size = 16, face = "bold", hjust = 0.5),
  plot.subtitle = element_text(color = "blue", hjust = 0.5),
  plot.caption = element_text(color = "black", size = 12, hjust = 0.5))
```
</center>

### FIG 4
<center>
``` {r echo=FALSE}
# This plot displays a 3 learning curve plots of 1-10 trials using the response function and data from strudel analysis.

# Variables for response function
alpha = .20
fixedTasks = 26
learnedTasks = 32.75

# Data frame is the data structure used to store data for visualize plots 
multi_learning_curve = data.frame(
  labels = c(1:10),
  respFunc = fixedTasks + (learnedTasks*((c(1:10))^-alpha)),#Function working for this
  respFunc2 = c(40.5,37.4,36,35.2,34.6,34.1,33.8,33.5,33.2,33),#Change to working function
  respFunc3 = c(23.3,14.5,13.1,12.4,12,11.7,11.5,11.3,11.1,11)#Change to working function
)

# Visualization and construction of plot
ggplot(multi_learning_curve, aes(x = labels)) + 
  geom_line(aes(y = respFunc, color="High", group= 1), size = 2) +
  geom_line(aes(y = respFunc2, color="Low", group= 2), size = 2) +
  geom_line(aes(y = respFunc3, color="Low-to-High", group= 3), size = 2) +
  labs(x = "Trials", y = "Response Time (s)",
       title = "Multi-Complex Learning Curve Plot", 
       subtitle = "Figure 4",
       caption = "Figure 4: This plot displays a 3 learning curve plots of 1-10 trials.") + 
  scale_x_continuous(breaks=c(1:10)) +
  theme_light() + 
  theme(legend.title=element_blank(), 
  plot.title = element_text(color = "red", size = 16, face = "bold", hjust = 0.5),
  plot.subtitle = element_text(color = "blue", hjust = 0.5),
  plot.caption = element_text(color = "black", size = 12, hjust = 0.5))

```
</center>

### FIG 5
<center>
``` {r echo=FALSE}
# This plot displays fault mixed learning plot using the data from strudel analysis.

# Data frame is the data structure used to store data for visualize plots 
fault_mixed_learning_plot = data.frame(
  labels = c("Low", "High", "HHap", "RWhu", "RWHap"),
  data = c(23.3,58.75,0,0,0)
)

sorted_labels = factor(fault_mixed_learning_plot$labels,levels = c("Low", "High", "HHap", "RWhu", "RWHap"))# Sorts labels using factor function 

# Visualization and construction of plot
ggplot(fault_mixed_learning_plot, aes(x = sorted_labels, y = data, color=sorted_labels, group= 1)) + 
  geom_line() +
  geom_point(size = 4) +
  labs(x = "Interface Type",y = "Time Per Trial",
       title = "Simple Fault Mixed Learning Plot", 
       subtitle = "Figure 5",
       caption = "Figure 5: This plot displays fault mixed learning plot.") + 
  theme_bw() + 
  theme(legend.title=element_blank(), 
  plot.title = element_text(color = "red", size = 16, face = "bold", hjust = 0.5),
  plot.subtitle = element_text(color = "blue", hjust = 0.5),
  plot.caption = element_text(color = "black", size = 12, hjust = 0.5))
```
</center>

### FIG 6
<center>
``` {r echo=FALSE}
# This plot displays a second fault mixed learning plot using the data from strudel analysis.

# Data frame is the data structure used to store data for visualize plots 
fault_mixed_learning_plot_v2 = data.frame(
  labels = c("Low", "High", "HHap", "RWhu", "RWHap"),
  data = c(2.6,1,0,0,0)
)

sorted_labels = factor(fault_mixed_learning_plot_v2$labels,levels = c("Low", "High", "HHap", "RWhu", "RWHap"))# Sorts labels using factor function 

# Visualization and construction of plot
ggplot(fault_mixed_learning_plot_v2, aes(x = sorted_labels, y = data, color=sorted_labels, group= 1)) + 
  geom_line() +
  labs(x = "Interface Type", y = "Time Per Trial",
       title = "Simple Fault Mixed Learning Plot v2", 
       subtitle = "Figure 6",
       caption = "Figure 6: This plot displays a second fault mixed learning plot.") + 
  geom_point(size = 4) +
  theme_gray()+ 
  theme(legend.title=element_blank(), 
  plot.title = element_text(color = "red", size = 16, face = "bold", hjust = 0.5),
  plot.subtitle = element_text(color = "blue", hjust = 0.5),
  plot.caption = element_text(color = "black", size = 12, hjust = 0.5))

```
</center>

### FIG 7
<center>
``` {r echo=FALSE}
# This plot displays an interface combination plot using the data from strudel analysis.

rand_values = runif(2000, min=0, max=61)#Generates Random Values N=2000, i = 0-61

# Data frame is the data structure used to store data for visualize plots 
ui_combo_plot = data.frame(
  id = c(1:8),
  ui_combo = 	c("Lhu","LHap","Mhu","Mhap","Hhu","HHap","RWhu","RWHap"),		
  time_per_trial = c(11.75,12.95,15.95,15.95,13.75,35.4,60.25,60.25), 
  stringsAsFactors = FALSE
)
sorted_labels = factor(ui_combo_plot$ui_combo,levels = c("Lhu","LHap","Mhu","Mhap","Hhu","HHap","RWhu","RWHap"))

# Visualization and construction of plot
ggplot(ui_combo_plot, aes(sorted_labels,time_per_trial, group = 1, color=sorted_labels))+
  geom_line(color='black',size=1) +
  geom_point(size = 4) +
  labs(x = "User Interface Combination", y = "Times Per Trial (s)",
       title = "User Interface Combination Plot", 
       subtitle = "Figure 7",
       caption = "Figure 7: This plot displays an interface combination plot.") + 
  theme_gray() + 
  theme(legend.title=element_blank(), 
  plot.title = element_text(color = "red", size = 16, face = "bold", hjust = 0.5),
  plot.subtitle = element_text(color = "blue", hjust = 0.5),
  plot.caption = element_text(color = "black", size = 12, hjust = 0.5))
```
</center>

### FIG 8
<center>
``` {r echo=FALSE}
# This plot displays an second interface combination plot using the data from strudel analysis.

# Data frame is the data structure used to store data for visualize plots 
ui_combo_plot_v2 = data.frame(
  id = c(1:8),
  ui_combo = 	c("Lhu","LHap","Mhu","Mhap","Hhu","HHap","RWhu","RWHap"),		
  time_per_trial = c(4.6,4.6,3.8,3.8,1.7,1.7,1,1)
)
sorted_labels = factor(ui_combo_plot_v2$ui_combo,levels = c("Lhu","LHap","Mhu","Mhap","Hhu","HHap","RWhu","RWHap"))

# Visualization and construction of plot
ggplot(ui_combo_plot_v2, aes(sorted_labels,time_per_trial, group = 1, color=sorted_labels))+
  geom_line(color='black',size=1) +
  geom_point(size = 4) +
  labs(x = "User Interface Combination", y = "Times Per Trial (s)",
       title = "User Interface Combination Plot v2", 
       subtitle = "Figure 8",
       caption = "Figure 8: This plot displays an second interface combination plot.") + 
  theme_minimal() + 
  theme(legend.title=element_blank(), 
  plot.title = element_text(color = "red", size = 16, face = "bold", hjust = 0.5),
  plot.subtitle = element_text(color = "blue", hjust = 0.5),
  plot.caption = element_text(color = "black", size = 12, hjust = 0.5))
```
</center>

### FIG 9
<center>
``` {r echo=FALSE, message=FALSE}
# This plot displays a random plot of 10 trials 

# Random Plot 
efforts = runif(10, min=0, max=10)

# Data frame is the data structure used to store data for visualize plots 
logPlot = data.frame(
  eff = efforts,
  Y = c(1:10)
)

# Visualization and construction of plot
ggplot(data = logPlot, aes(x = efforts, y = Y, color=Y)) +
  geom_line() +
  geom_point() +
  labs(x = "Trials", y = "Response Time",
       title = "Random Plot", 
       subtitle = "Figure 9",
       caption = "Figure 9: This plot displays a random plot of 10 trials.") + 
  scale_x_continuous(breaks=c(1:10)) +
  scale_y_continuous(breaks=c(1:10)) +
  geom_smooth(method = "lm", se = FALSE)  + 
  theme(
  plot.title = element_text(color = "red", size = 16, face = "bold", hjust = 0.5),
  plot.subtitle = element_text(color = "blue", hjust = 0.5),
  plot.caption = element_text(color = "black", size = 12, hjust = 0.5))

#https://holtzy.github.io/Pimp-my-rmd/#tabs_for_sub-chapters
```

### FIG 10
<center>
``` {r echo=FALSE, message=FALSE}
# This plot displays an log plot using the data from strudel analysis.

efforts = runif(10, min=0, max=10)

# Data frame is the data structure used to store data for visualize plots 
logPlot = data.frame(
  eff = efforts,
  Y = c(1:10)
)

# Visualization and construction of plot
ggplot(data = logPlot, aes(x = efforts, y = Y, color=Y)) + 
  geom_line() +
  geom_point() +
  scale_x_continuous(breaks=c(1:10)) +
  scale_y_continuous(breaks=c(1:10)) +
  labs(x = "Trials", y = "Response Time",
       title = "Log Log Plot", 
       subtitle = "Figure 10",
       caption = "Figure 10: This plot displays an log plot.") + 
  geom_smooth(method = "lm", se = FALSE) + 
  theme(
  plot.title = element_text(color = "red", size = 16, face = "bold", hjust = 0.5),
  plot.subtitle = element_text(color = "blue", hjust = 0.5),
  plot.caption = element_text(color = "black", size = 12, hjust = 0.5))

# !!! add descriptions to graphs, and change names of tabs

#https://holtzy.github.io/Pimp-my-rmd/#tabs_for_sub-chapters
```

``` {r echo=FALSE, message=FALSE}
# SOURCES
# [1] https://holtzy.github.io/Pimp-my-rmd/#tabs_for_sub-chapters
# [2] https://en.wikipedia.org/wiki/Power_law_of_practice
```

</center>

## {-}

&nbsp;
<hr />
<h4 style="text-align: center;">Programming done by <a href="https://github.com/gremlokk/">Fredrick Ryans</a></h4>
<h4 style="text-align: center;"><span style="color: #808080;">Email: <em>fxr5077@psu.edu</em></span></h4>
<h4 style="text-align: center;"><a href="http://acs.ist.psu.edu/wp/"> >> Applied Cognitive Science Lab << </a></h4>

<!-- Add icon library -->
<link rel="stylesheet" href="https://cdnjs.cloudflare.com/ajax/libs/font-awesome/4.7.0/css/font-awesome.min.css">

<!-- Add font awesome icons -->
<h2 style="text-align: center;">
    <a href="https://www.linkedin.com/in/fryans" target = "_blank" class="fa fa-linkedin"></a>
    <a href="https://github.com/gremlokk/" target = "_blank" class="fa fa-github"></a>
</h2>

&nbsp;
