---
title: "STRUDEL FIDELITY RESEARCH ANALYSIS"
author: "Dr. Ritter, Fredrick Ryans, Martin Yeh"
date: "8/14/2020"
output:
  html_document:
    df_print: paged
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### **NOTES & UPDATES**
 This document is a visual analysis of the Strudel data models provided
 in the Ritter paper: fidelity on learning.

##### *Link To Paper:* [Click Here](http://acs.ist.psu.edu/papers/ritterM20.pdf)

**MAJOR UPDATES**

* **Update 07/28/20**
  + Successfully sorted categorical data with factor function
  + Added more plots & better visualization aspects

* **Update 08/05/20** 
  + Added comments
  + Updated variables to be more description
  + Added more plots & better visualization aspects
  + Add default legend name, and key (no documentation found on this that works)
  + Learn to plot
 Read log/log plot and create complex graph
 Help function: help("ggplot")
 Change code to reflect 

* **Update 08/11/20**
  + ! Need to change plot number system from double to int on x/y axis. 
  + ! unsuccessful with reading alpha input for various value calculations
  + Save plots via code ggplot(), next phase to generate automated reports 
  + Corrected x,y axis labels to
  + ! Reading on log log plots, and trying to compute 
 Change legend title to blank

```{r}
#library(dplyr)
library(ggplot2)
library(tidyr)

options(max.print=1000000)

```
  
  
#### **PLOT ANALYSIS**  


```{r echo=FALSE}
alpha = 0.02
fixedTasks = 26
learnedTasks = 32.75

learning_curve = data.frame(
  labels = c(1:10),
  respFunc = fixedTasks + (learnedTasks*((c(1:10))^-alpha))
)

ggplot(learning_curve, aes(x = labels, y = respFunc)) +
  labs(x = "Trials", y = "Response Time") + #response time, task time
  geom_line(color="green", size=1) +
  geom_point(size = 2) +
  ggtitle("Learning Curve Plot")

```

``` {r echo=FALSE}
#Larger Learning Curve Plot 1-2000----------------------------------------------
larger_learning_curve = data.frame(
  labels = c(1:2000),
  respFunc = fixedTasks + (learnedTasks*((c(1:2000))^-alpha))
)

ggplot(larger_learning_curve, aes(x = labels, y = respFunc)) + 
  labs(x = "Trials", y = "Response Time") +
  geom_line() +
  geom_point(size=1) +
  ggtitle("Larger Learning Curve Plot (1-2000 Datapoints)") +
  theme_bw()

```

``` {r echo=FALSE}
#Two Line Lofi Hifi Plot--------------------------------------------------------
two_line_plot = data.frame( #Use function to generate plots
  time_blocks = c(1:10),
  lofi_resp_time = c(11.8,5.5,4.3,3.8,3.5,3.2,3.1,2.9,2.8,2.7),
  hifi_resp_time = c(13.75,7.807,5.544,4.756,4.316,4.022,3.805,3.635,3.497,3.382)
)

ggplot(two_line_plot, aes(x=time_blocks)) +
  geom_line(aes(y=lofi_resp_time, color="Lofi"), size = 1)+ 
  geom_line(aes(y=hifi_resp_time,color="Hifi"),size=1) + 
  labs(x = "Trials", y = "Response Time") +
  ggtitle("Figure 3: HiFi and LoFi Curves") +
  theme_bw() + 
  theme(legend.title=element_blank())
```

``` {r echo=FALSE}
#Multi-Learning Curve Plot------------------------------------------------------
alpha = .20
fixedTasks = 26
learnedTasks = 32.75

multi_learning_curve = data.frame(
  labels = c(1:10),
  respFunc = fixedTasks + (learnedTasks*((c(1:10))^-alpha)),#Function working for this
  respFunc2 = c(40.5,37.4,36,35.2,34.6,34.1,33.8,33.5,33.2,33),#Change to working function
  respFunc3 = c(23.3,14.5,13.1,12.4,12,11.7,11.5,11.3,11.1,11)#Change to working function
)

ggplot(multi_learning_curve, aes(x = labels)) + 
  labs(x = "Trials", y = "Response Time") +
  geom_line(aes(y = respFunc, color="High", group= 1), size = 2) +
  geom_line(aes(y = respFunc2, color="Low", group= 2), size = 2) +
  geom_line(aes(y = respFunc3, color="Low-to-High", group= 3), size = 2) +
  ggtitle("Multi-Complex Learning Curve Plot") +
  coord_cartesian(xlim = c(1, 10), ylim = c(0, 75)) +
  theme_light() + 
  theme(legend.title=element_blank())

```

``` {r echo=FALSE}
#Simple Fault Mixed Learning Plot Figure 1--------------------------------------
fault_mixed_learning_plot = data.frame(
  labels = c("Low", "High", "HHap", "RWhu", "RWHap"),
  data = c(23.3,58.75,0,0,0)
)

sorted_labels = factor(fault_mixed_learning_plot$labels,levels = c("Low", "High", "HHap", "RWhu", "RWHap"))# (Funky Sort solution to be optmz)

ggplot(fault_mixed_learning_plot, aes(x = sorted_labels, y = data, color=sorted_labels, group= 1)) + 
  labs(x = "Interface Type",y = "Time Per Trial") +
  geom_line() +
  geom_point(size = 4) +
  ggtitle("Simple Fault Mixed Learning Plot: Figure 1") +
  theme_bw() + 
  theme(legend.title=element_blank())
```

``` {r echo=FALSE}
#Simple Fault Mixed Learning Plot Figure 2--------------------------------------
fault_mixed_learning_plot_v2 = data.frame(
  labels = c("Low", "High", "HHap", "RWhu", "RWHap"),
  data = c(2.6,1,0,0,0)
)

sorted_labels = factor(fault_mixed_learning_plot_v2$labels,levels = c("Low", "High", "HHap", "RWhu", "RWHap"))# (Funky Sort solution to be optmz)

ggplot(fault_mixed_learning_plot_v2, aes(x = sorted_labels, y = data, color=sorted_labels, group= 1)) + 
  labs(x = "Interface Type",y = "Time Per Trial") +
  geom_line() +
  geom_point(size = 4) +
  ggtitle("Simple Fault Mixed Learning Plot:Figure 2") +
  theme_gray()+ 
  theme(legend.title=element_blank())


```

``` {r echo=FALSE}
# User Interface Combination Plots-----------------------------------------------
rand_values = runif(2000, min=0, max=61)#Generates Random Values N=2000, i = 0-61

# User Interface Combination Plots: Figure 1
ui_combo_plot = data.frame(
  id = c(1:8),
  ui_combo = 	c("Lhu","LHap","Mhu","Mhap","Hhu","HHap","RWhu","RWHap"),		
  time_per_trial = c(11.75,12.95,15.95,15.95,13.75,35.4,60.25,60.25), 
  stringsAsFactors = FALSE
)
sorted_labels = factor(ui_combo_plot$ui_combo,levels = c("Lhu","LHap","Mhu","Mhap","Hhu","HHap","RWhu","RWHap"))

ggplot(ui_combo_plot, aes(sorted_labels,time_per_trial, group = 1, color=sorted_labels))+
  geom_line(color='black',size=1) +
  geom_point(size = 4) +
  ylab("Times Per Trial (s)") +
  xlab("User Interface Combination") +
  ggtitle("Figure 1") +
  theme_gray() + 
  theme(legend.title=element_blank())
```

``` {r echo=FALSE}
# User Interface Combination Plots: Figure 2
ui_combo_plot_v2 = data.frame(
  id = c(1:8),
  ui_combo = 	c("Lhu","LHap","Mhu","Mhap","Hhu","HHap","RWhu","RWHap"),		
  time_per_trial = c(4.6,4.6,3.8,3.8,1.7,1.7,1,1)
)
sorted_labels = factor(ui_combo_plot_v2$ui_combo,levels = c("Lhu","LHap","Mhu","Mhap","Hhu","HHap","RWhu","RWHap"))

ggplot(ui_combo_plot_v2, aes(sorted_labels,time_per_trial, group = 1, color=sorted_labels))+
  geom_line(color='black',size=1) +
  geom_point(size = 4) +
  ylab("Times Per Trial (s)") +
  xlab("User Interface Combination") +
  ggtitle("Figure 2") +
  theme_minimal() + 
  theme(legend.title=element_blank())
```